Deployable Probabilistic Programming

### 2019-04-16 paper/paper.tex
conclusion

A lightweight probabilistic programming facility similar to
Infergo can be added to most modern general-purpose programming
languages, in particular those used in implementing large-scale
software systems, making probabilistic programming inference
more accessible in server-side applications.

>>>>

Building a production software system which employs
probabilistic inference as an integral part of prediction and
decision making algorithms is challenging. To address the
challenges, we proposed guidelines for implementation of a
deployable probabilistic programming facility. Further on, we
introduced Infergo, a probabilistic programming facility in Go,
as a reference implementation following the guidelines. Infergo
allows to program inference models in virtually unrestricted Go,
and to perform inference on the model using either supplied or
third-party algorithms. We demonstrated on case studies how
Infergo overcomes the challenges by following the guidelines.

A probabilistic programming facility similar to Infergo can be
added to most modern general programming languages, in
particular, those used in implementing large-scale software
systems, making probabilistic programming inference more
accessible in server-side applications. We described Infergo
design choices and implementation techniques in intent to
encourage broader adoption of probabilistic programming in
production software systems and ease implementation of similar
facilities in other languages and software environments.

Infergo is an ongoing project. Development of Infergo is
influenced both by feedback from the open-source Go community
and by the needs of the software system in which Infergo was
initially deployed, and which still supplies the most demanding
use cases in terms of flexibility, scalability, and ease of
integration and maintenance. Deploying probabilistic programming
as a part of production software system has a mutual benefit of
both improving the core algorithms of the system and of helping
to shape and improve probabilistic modeling and inference, thus
further advancing the field of probabilistic programming.
